\pdfminorversion=5 % To enforce 1.5 version of PDF
\input{src/header}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% TITLE PAGE PARAMETERS
\title{Version Control Workshop: Git and GitHub}
\subtitle{~}
\institute{Purdue University}
\author[AUTHOR]{\scriptsize{Cyrus Vandrevala $^1$\\Nicol\'as Guar\'in-Zapata$^2$}\\
\tiny{$^1$ Physics Department\\ $^2$ Civil Engineering Department}}
\date{October 30-31, 2014}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% TITLEPAGE
\begin{frame}[plain]
  \titlepage
\end{frame}

% OVERVIEW
\begin{frame}
\frametitle{\large{Overview}}
\begin{enumerate}
\item Introduction to Version Control
\item Workflow in Computational Science
\item Learning Git
\begin{itemize}
\item Setting Up Git On Your Machine
\item Basic Git Cycle
\item Git Branches
\item Git Delete Commands
\end{itemize}
\item Git and GitHub
\item Collaborated Summary
\end{enumerate}
\end{frame}

% ======================================= %
% INTRODUCTION TO VERSION CONTROL
% ======================================= %

% WHAT IS VERSION CONTROL?
\begin{frame}
\frametitle{\large{What is Version Control?}}
Version control is a system that records changes to a file or set of files over time so that you can recall specific versions later.
\end{frame}

% WHY IS VERSION CONTROL IMPORTANT?
\begin{frame}
\frametitle{\large{Why is Version Control Important?}}
\begin{enumerate}
\item Keep Track of Code History
\pause
\item Concurrent Teamwork
\pause
\item Coordinating Development, Testing, Deployment, etc.
\pause
\item Due Diligence Checks
\pause
\item Structuring the Way You Develop Code
\pause
\item Sharing Code
\end{enumerate}
\pause
Everybody should use version control!
\end{frame}

% WHAT OPTIONS ARE AVAILABLE? (part 1)
\begin{frame}
\frametitle{\large{What Options Are Available?}}
\textbf{Option \#1: Client-Server Version Control Systems}
\linebreak
\begin{columns}[c]
\column{2in}
\textbf{Advantages}
\begin{enumerate}
\item A Single Admin Keeps Track of the Project
\item There is a Single Master Version of the Code
\item A Central Server Can Be Created for the Project
\end{enumerate}
\column{2in}
\textbf{Disadvantages}
\begin{enumerate}
\item There Is Only One Admin
\item You Need a Network Connection to Work
\item Operations Can Be Slow (You Need to Access a Central Server)
\end{enumerate}
\end{columns}
\vspace{5mm}
Examples include CVS
\end{frame}

% WHAT OPTIONS ARE AVAILABLE? (part 2)
\begin{frame}
\frametitle{\large{What Options Are Available?}}
\textbf{Option \#1: Distributed Version Control Systems}
\linebreak
\begin{columns}[c]
\column{2in}
\textbf{Advantages}
\begin{enumerate}
\item It is Easy to Work Without a Network Connection
\item Multiple Branches Can Provide Multiple Environments
\item You Do Not Need an Internet Connection (Until Committing)
\end{enumerate}
\column{2in}
\textbf{Disadvantages}
\begin{enumerate}
\item It is a More Sophisticated System
\item People Need to Talk More
\item It Is *Really* Easy To Create Unorganized Code 
\end{enumerate}
\end{columns}
\vspace{5mm}
Examples include Git and Bazaar
\end{frame}

% WHY GIT AND GITHUB?
\begin{frame}
\frametitle{\large{Why Git and GitHub?}}
\begin{enumerate}
\item It Has a Great Social Community
\item It Keeps Track of Detailed Metadata (More Than SVN)
\item Branching is Encouraged and Modularizes Development
\end{enumerate}
\end{frame}

% ======================================= %
% WORKFLOW IN COMPUTER SCIENCE
% ======================================= %


% ===================================================================== %
% CHAPTER -1 : Last Frame
% ===================================================================== %
\frame{
\frametitle{\large{}}
	\huge{\center{\color{RUBblau}{Thank you for your attention.}}}
}

\end{document}
