\pdfminorversion=5 % To enforce 1.5 version of PDF

\input{src/header}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% TITLE PAGE PARAMETERS
\title{Version Control Workshop: Git and GitHub}
\subtitle{Day 1}
\institute{Purdue University}
\author[AUTHOR]{\scriptsize{Cyrus Vandrevala $^1$\\Nicol\'as Guar\'in-Zapata$^2$}\\
\tiny{$^1$ Physics Department\\ $^2$ Civil Engineering Department}}
\date{October 30-31, 2014}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% TITLEPAGE
\begin{frame}[plain]
  \titlepage
\end{frame}

% OVERVIEW
%\begin{frame}
%\frametitle{\large{Overview}}
%\begin{enumerate}
%\item Introduction to Version Control
%\item Workflow in Computational Science
%\item Learning Git
%\begin{itemize}
%\item Setting Up Git On Your Machine
%\item Basic Git Cycle
%\item Git Branches
%\item Git Delete Commands
%\end{itemize}
%\item Git and GitHub
%\item Collaborated Summary
%\end{enumerate}
%\end{frame}

\begin{frame}
\frametitle{\large{Overview}}
\tableofcontents
\end{frame}

\begin{frame}
\frametitle{\large{Disclaimer}}

\end{frame}

% ======================================= %
% INTRODUCTION TO VERSION CONTROL
% ======================================= %

\section[Intro]{Introduction to Version Control}

% WHAT IS VERSION CONTROL?
\begin{frame}
\frametitle{\large{What is Version Control?}}
Version control is a system that records changes to a file or set of files over time so that you can recall specific versions later.
\end{frame}

% WHY IS VERSION CONTROL IMPORTANT?
\begin{frame}
\frametitle{\large{Why is Version Control Important?}}
\begin{enumerate}
\item Keep Track of Code History
\pause
\item Concurrent Teamwork
\pause
\item Coordinate Coding Environments
\pause
\item Due Diligence Checks
\pause
\item Share Code
\end{enumerate}
\pause
\vspace{5mm}
Everybody Should Use Version Control!
\end{frame}

% WHAT OPTIONS ARE AVAILABLE? (part 1)
\begin{frame}
\frametitle{\large{What Options Are Available?}}
\textbf{Option \#1: Client-Server Version Control Systems}
\vspace{8mm}
\begin{columns}[c]
\column{2in}
{\small \textbf{Advantages}}
\begin{enumerate}
\small 
\item A Single Admin Keeps Track of the Project
\item There is a Single Master Version of the Code
\item It is Relatively Easy to Learn
\end{enumerate}
\column{2in}
{\small \textbf{Disadvantages} }
\begin{enumerate}
\small
\item There Is Only One Admin/Server
\item You Need a Network Connection to Work
\item Operations Can Be Slow
\end{enumerate}
\end{columns}
\vspace{5mm}
{\small Examples include Concurrent Versions System (CVS) and Subversion (SVN).}
\end{frame}

% WHAT OPTIONS ARE AVAILABLE? (part 2)
\begin{frame}
\frametitle{\large{What Options Are Available?}}
\textbf{Option \#2: Distributed Version Control Systems}
\vspace{8mm}
\begin{columns}[c]
\column{2in}
{\small \textbf{Advantages}}
\begin{enumerate}
\small
\item You Don't Need a Network Connection
\item Multiple Coding Environments
\item It Encourages Collaboration and Modularity
\end{enumerate}
\column{2in}
{\small \textbf{Disadvantages}}
\begin{enumerate}
\small
\item Can Be Difficult to Learn
\item Teams Need to Talk About Conventions
\item It is Really Easy To Create Unorganized Code 
\end{enumerate}
\end{columns}
\vspace{5mm}
{\small Examples include Git/GitHub and Bazaar.}
\end{frame}

% WHY GIT AND GITHUB? (part 1)
\begin{frame}
\frametitle{\large{Why Git and GitHub?}}
\begin{enumerate}
\item It Keeps Track of Detailed Metadata (More Than Others)
\item Branching is Encouraged (Which Modularizes Development)
\item GitHub Has a Great Social Community
\end{enumerate}
\end{frame}

% WHY GIT AND GITHUB? (part 2)
\begin{frame}
\frametitle{\large{Why Git and GitHub?}}
Full Disclosure...
\begin{enumerate}
\item It Isn't the Best for Binary Files
\item GitHub Distinguishes Between Public and Private Repos
\end{enumerate}
\end{frame}

% ======================================= %
% WORKFLOW IN COMPUTER SCIENCE
% ======================================= %
\section[SciComp Work Flow]{Work Flow in Computational Science}

\begin{frame}
\frametitle{\large{Version Control in Academia}}
\begin{enumerate}
\item It Creates Reproducible Research
\item It Helps Train New Group Members
\item It Encourages Collaboration
\item It Encourages Good Code Practices
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{\large{Version Control in Academia}}
Some Useful Skills That You Should Learn Are:
\begin{enumerate}
\item Bash
\item Markdown
\end{enumerate}
\end{frame}

% ======================================= %
% SETTING UP GIT
% ======================================= %

\section[Setting Up Git]{Setting Up Git On Your Machine}

\begin{frame}
\frametitle{\large{Setting Up Git - Linux}}
You can use the package management tool that comes with your distribution (use sudo):
\begin{enumerate}
\item yum install git
\item apt-get install git
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{\large{Setting Up Git - Mac}}
There are three main ways to install Git:
\begin{enumerate}
\item Install the Xcode Command Line Tools and Type "git" Into the Terminal
\item Binary Installer: \href{http://git-scm.com/download/mac}{http://git-scm.com/download/mac}
\item Git/GitHub GUI: \href{https://mac.github.com/}{https://mac.github.com/}
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{\large{Setting Up Git - Windows}}
There are three main ways to install Git:
\begin{enumerate}
\item Binary Installer: \href{http://git-scm.com/download/win}{http://git-scm.com/download/win}
\item msysGit: \href{http://msysgit.github.io/}{http://msysgit.github.io/}
\item Git/GitHub GUI: \href{https://windows.github.com/}{https://windows.github.com/}
\end{enumerate}
\end{frame}

% ======================================= %
% BASIC GIT
% ======================================= %

\section[Basic Git]{Basic Git Work Flow}

\begin{frame}
    \frametitle{The Git Cycle}
    \begin{enumerate}
    \item Synchronize Version (git pull)\pause
    \item Make Changes to Code \pause
    \item Stage Changes for Commit (git add) \pause
    \item Commit Changes (git commit) \pause
    \item Push to Origin (git push) \pause
    \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{ Review Changes}
    View Log (git log)
    
    View Staged Changes (git status)
\end{frame}

    
\begin{frame}
    \frametitle{Recovering Past Versions}
    Organizing Past Versions (MD5 Hash)
    
    Recovering a Previous Version (git checkout )
\end{frame}
    
    
\section[Branches]{Git Branches}
% ======================================= %
% BRANCHES
% ======================================= %

\begin{frame}
    \frametitle{What is Branching?}
\end{frame}

\begin{frame}
    \frametitle{Create a New Branch (git checkout -b)}
\end{frame}

\begin{frame}
    \frametitle{Merge Two Branches (git merge)}
\end{frame}

\begin{frame}
    \frametitle{Synchronize Two Branches (git rebase)}
\end{frame}

\begin{frame}
    \frametitle{List All Branches (git branch)}
\end{frame}


\section[Delete]{Git Delete Commands}
% ======================================= %
% GIT DELETE
% ======================================= %
\begin{frame}
    \frametitle{Delete a File (rm vs. git rm)}
\end{frame}

\begin{frame}
    \frametitle{Delete a File (rm vs. git rm)}
\end{frame}

\begin{frame}
    \frametitle{Undoing Changes (git revert vs. git reset)}
\end{frame}


\section[GitHub]{Combining Git With GitHub}
\begin{frame}
    \frametitle{Public vs. Private Repositories}
    Bitbucket and GitHub
\end{frame}

\begin{frame}
    \frametitle{Set Up Git Remote}
\end{frame}


\begin{frame}
    \frametitle{Review the Git Cycle}
\end{frame}

\begin{frame}
    \frametitle{Pull Requests}
    Forking a Repository
\end{frame}


% ===================================================================== %
% COLLABORATED SUMMARY
% ===================================================================== %
\begin{frame}
\frametitle{\large{}}
	\huge{\center{\color{RUBblau}{Thank you for your attention.}}}
\end{frame}

% Add a questions section to the summary so you can answer any questions on day 2

\end{document}
