% ======================================= %
% INTRODUCTION TO VERSION CONTROL
% ======================================= %

\section[Introduction]{Introduction to Version Control}

% WHAT IS VERSION CONTROL?
\begin{frame}
\frametitle{\large{What is Version Control?}}
Version control is a system that records changes to a file or set of files over time so that you can recall specific versions later. \\
\vspace{3mm}
- \emph{Pro Git}, Chapter 1
\end{frame}
\note{}

\begin{frame}
\frametitle{\large{What is Version Control?}}
It allows you to revert files back to a previous state, revert the entire project back to a previous state, compare changes over time, see who last modified something that might be causing a problem, who introduced an issue and when, and more. \\
\vspace{3mm}
- \emph{Pro Git}, Chapter 1
\end{frame}
\note[itemize]{
\item One of the first major version control systems was the Revision Control System (RCS). It was released by Walter F. Tichy while he was at Purdue University (RCS: A System for Version Control).
}

% WHY IS VERSION CONTROL IMPORTANT?
\begin{frame}
\frametitle{\large{Why is Version Control Important?}}
\begin{enumerate}
\item Keep Track of Code History
\pause
\item Concurrent Teamwork
\pause
\item Coordinate Coding Environments
\pause
\item Due Diligence Checks
\pause
\item Share Code
\end{enumerate}
\pause
\vspace{5mm}
Everybody Should Use Version Control!
\end{frame}
\note{}

% WHAT OPTIONS ARE AVAILABLE? (part 1)
\begin{frame}
\frametitle{\large{What Options Are Available?}}
\textbf{Option \#1: Client-Server Version Control Systems}
\vspace{8mm}
\begin{columns}[c]
\column{2in}
{\small \textbf{Advantages}}
\begin{enumerate}
\small
\item A Single Admin Keeps Track of the Project
\item There is a Single Master Version of the Code
\item It is Relatively Easy to Learn
\end{enumerate}
\column{2in}
{\small \textbf{Disadvantages} }
\begin{enumerate}
\small
\item There Is Only One Admin/Server
\item You Need a Network Connection to Work
\item Operations Can Be Slow
\end{enumerate}
\end{columns}
\vspace{5mm}
{\small Examples include Concurrent Versions System (CVS) and Subversion (SVN).}
\end{frame}
\note{}

% WHAT OPTIONS ARE AVAILABLE? (part 2)
\begin{frame}
\frametitle{\large{What Options Are Available?}}
\textbf{Option \#2: Distributed Version Control Systems}
\vspace{8mm}
\begin{columns}[c]
\column{2in}
{\small \textbf{Advantages}}
\begin{enumerate}
\small
\item You Don't Need a Network Connection
\item Multiple Coding Environments
\item It Encourages Collaboration and Modularity
\end{enumerate}
\column{2in}
{\small \textbf{Disadvantages}}
\begin{enumerate}
\small
\item Can Be Difficult to Learn
\item Teams Need to Talk About Conventions
\item It is Really Easy To Create Unorganized Code
\end{enumerate}
\end{columns}
\vspace{5mm}
{\small Examples include Git, Mercurial, and Bazaar.}
\end{frame}
\note{}

% WHY GIT AND GITHUB? (part 1)
\begin{frame}
\frametitle{\large{Why Git and GitHub?}}
\begin{enumerate}
\item It Keeps Track of Detailed Metadata (More Than Others)
\item Branching is Encouraged (Which Modularizes Development)
\item Most Operations in Git are Local (Which Increases Speed)
\item GitHub Has a Great Social Community
\end{enumerate}
\end{frame}
\note{}

% WHY GIT AND GITHUB? (part 2)
\begin{frame}
\frametitle{\large{Why Git and GitHub?}}
Full Disclosure...
\begin{enumerate}
\item It Isn't the Best for Binary Files
\item GitHub Distinguishes Between Public and Private Repos
\end{enumerate}
\end{frame}
\note{}
